---
title: "CaseStudyFinal"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
mydataset<-read.csv("BestBuy.csv")
summary(mydataset)
hist(mydataset$Warranty)

#install.packages("sqldf")
library(sqldf)
testsql=sqldf("select age,newcustomer from mydataset where newcustomer=1")

#Summary Statistics
hist(mydataset$PriceCategory) #comparing the histograms of key independent variable which are not dummy/factor variables
hist(log(mydataset$PriceCategory))
hist(mydataset$hhincome) #comparing the histograms of key independent variable which are not dummy/factor variables
hist(log(mydataset$hhincome))

#checking for multicollinearity
library(usdm)
df=data.frame(mydataset$newcustomer,mydataset$age,mydataset$hisp,mydataset$PriceCategory,mydataset$married,mydataset$MyBestBuy,mydataset$hhincome,mydataset$appliances,mydataset$familysize,mydataset$productgeneration,mydataset$weekend)
vif(df)
cor(df)
df1=data.frame(mydataset$newcustomer,mydataset$age,mydataset$hisp,mydataset$PriceCategory,mydataset$married,mydataset$MyBestBuy,mydataset$hhincome,mydataset$appliances,mydataset$familysize,mydataset$weekend)
vif(df1)
cor(df1)
df2=data.frame(mydataset$newcustomer,mydataset$age,mydataset$hisp,mydataset$PriceCategory,mydataset$MyBestBuy,mydataset$hhincome,mydataset$appliances,mydataset$familysize,mydataset$weekend)
vif(df2)
cor(df2)

# Linear probability model

#our dependent variable is Warranty
#our Key Independent Variables are PriceCategory*appliances, hisp,hhincome,familysize
#our control variables are age, newcustomer, weekend
names(mydataset)

model1<- lm(Warranty~PriceCategory+newcustomer+age+hisp+MyBestBuy+hhincome+appliances+familysize+weekend,data =mydataset) 
summary(model1) #first attempt
model2<- lm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer+age+hisp+MyBestBuy+hhincome+appliances+familysize+weekend,data =mydataset)
summary(model2) #adding interaction variable

model2wl<- lm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familysize+weekend,data =mydataset)
summary(model2wl) # this is model2 using log(hhincome) --> we get an error because there are some 0 values (which are transformed into -inf)


predictedprobability_lm<-predict(model2) # let's look at the predicted probability of return for each observation in the data 
plot(mydataset$Warranty,predictedprobability_lm)
range(predictedprobability_lm) #negative values and values greater than one so this is wrong!

predictedprobability_lm<-predict(model2wl) # let's look at the predicted probability of return for each observation in the data 
plot(mydataset$Warranty,predictedprobability_lm)
range(predictedprobability_lm)

#Logit

library(MASS)
library(QuantPsyc)
library(aod)
library(ggplot2)
library(Rcpp)

#calculating ratio
sum(mydataset$Warranty==0)
sum(mydataset$Warranty==1)
a=1216/9
b=1990/9
min(a,b)


#Changing family size to dummy
mydataset$familydummy<-ifelse(mydataset$familysize>2,1,0)

#model with interaction
logit1<-glm(Warranty~PriceCategory+newcustomer+age+hisp+MyBestBuy+hhincome+appliances+familysize+weekend,data =mydataset,family = "binomial")
summary(logit1)

#model with interaction
logit2<-glm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer+age+hisp+MyBestBuy+hhincome+appliances+familysize+weekend,data =mydataset,family = "binomial")
summary(logit2)

#testing logit1 and logit
anova(logit1,logit2)

exp(coef(logit2))

with(logit2, null.deviance - deviance)
with(logit2, df.null - df.residual)
with(logit2, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit2, data=mydataset)
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#model with log(hhincome+1)
logit3<-glm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familysize+weekend,data =mydataset,family = "binomial") #added log hhincome
summary(logit3)


exp(coef(logit3))

with(logit3, null.deviance - deviance)
with(logit3, df.null - df.residual)
with(logit3, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

 
pred = predict(logit3, data=mydataset)
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)



#model with interaction and log(hhincome+1) and newcustomer
logit4<-glm(Warranty~PriceCategory+PriceCategory*appliances+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familydummy+weekend+newcustomer,data =mydataset,family = "binomial")
summary(logit4) # final model
exp(coef(logit4))
with(logit4, null.deviance - deviance)
with(logit4, df.null - df.residual)
with(logit4, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit4, data=mydataset, type="response")
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#testing
AIC(logit3, logit4)  
BIC(logit3, logit4)

#model with familydummy and familyfactor
mydataset$familyfactor<-factor(mydataset$familysize)
logit8<-glm(Warranty~PriceCategory+PriceCategory*appliances+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familyfactor+weekend+newcustomer,data =mydataset,family = "binomial")
summary(logit8) # final model
exp(coef(logit8))
with(logit4, null.deviance - deviance)
with(logit4, df.null - df.residual)
with(logit4, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit8, data=mydataset, type="response")
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#testing
AIC(logit8, logit4)  
BIC(logit8, logit4)

#trying interaction newcustomer*MyBestBuy
logit5<-glm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer*MyBestBuy+newcustomer+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familydummy+weekend,data =mydataset,family = "binomial")
summary(logit5) # with new customer*MyBestBuy

with(logit5, null.deviance - deviance)
with(logit5, df.null - df.residual)
with(logit5, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit5, data=mydataset, type="response")
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

anova(logit5,logit4, test="Chisq")

#trying interaction PriceCategory*familydummy
logit6<-glm(Warranty~PriceCategory+PriceCategory*familydummy+newcustomer+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familydummy+weekend,data =mydataset,family = "binomial")
summary(logit6) # with new customer*MyBestBuy

with(logit6, null.deviance - deviance)
with(logit6, df.null - df.residual)
with(logit6, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit6, data=mydataset, type="response")
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#testing
anova(logit6,logit4, test="Chisq")

#trying with quadratic
logit7<-glm(Warranty~PriceCategory+PriceCategory*appliances+age+hisp+MyBestBuy+log(hhincome+1)+I(log(hhincome+1)^2)+appliances+familydummy+weekend+newcustomer,data =mydataset,family = "binomial")
summary(logit7) # final model
exp(coef(logit7))
with(logit7, null.deviance - deviance)
with(logit7, df.null - df.residual)
with(logit7, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit7, data=mydataset, type="response")
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#model with familydummy and familyfactor
mydataset$familyfactor<-factor(mydataset$familysize)
logit8<-glm(Warranty~PriceCategory+PriceCategory*appliances+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familyfactor+weekend+newcustomer,data =mydataset,family = "binomial")
summary(logit8) # final model
exp(coef(logit8))
with(logit4, null.deviance - deviance)
with(logit4, df.null - df.residual)
with(logit4, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))


pred = predict(logit8, data=mydataset, type="response")
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#testing
AIC(logit8, logit4)  
BIC(logit8, logit4)

#select required rows
test<-subset(mydataset,hhincome>17 & hhincome<52,select =c("hhincome"))
nrow(test)

#heteroskedasticity
library(lmtest)
gqtest(logit4) 
bptest(logit4)

library(sandwich)
library(foreign)

coeftest(logit4, vcov = vcovHC(logit4, "HC1")) # With robust standard errors
summary(logit4)

##Predicted Probs

#Interaction interpretation
library(ggplot2)

newdatatest <- with(mydataset,data.frame(PriceCategory= rep(seq(from = 1, to = 17, length.out = 17),2), newcustomer=mean(newcustomer),age=mean(age),hisp=mean(hisp),MyBestBuy=mean(MyBestBuy),hhincome=mean(hhincome),appliances=(rep(0:1, each = 17)),weekend=mean(weekend),familydummy=mean(familydummy)))

newdatatest1 <- cbind(newdatatest, predict(logit4, newdata = newdatatest, type="link", se=TRUE))
newdatatest1 <- within(newdatatest1, {
  PredictedProb <- plogis(fit)
  LL <- plogis(fit - (1.96 * se.fit))
  UL <- plogis(fit + (1.96 * se.fit))})

head(newdatatest1)

ggplot(newdatatest1, aes(x = PriceCategory, y = PredictedProb))+
  geom_ribbon(aes(ymin = LL, ymax = UL, fill = factor(appliances)), alpha = .2) +
  geom_line(aes(colour = factor(appliances)), size=1)

#Hispanic
newdatatest_hisp <- with(mydataset,data.frame(hisp=(rep(0:1)),PriceCategory=mean(PriceCategory), newcustomer=mean(newcustomer),age=mean(age),MyBestBuy=mean(MyBestBuy),hhincome=mean(hhincome),appliances=mean(appliances),weekend=mean(weekend),familydummy=mean(familydummy)))

newdatatest_hisp1 <- cbind(newdatatest_hisp, predict(logit4, newdata = newdatatest_hisp, type="link", se=TRUE))
newdatatest_hisp1 <- within(newdatatest_hisp1, {
  PredictedProb <- plogis(fit)
  LL <- plogis(fit - (1.96 * se.fit))
  UL <- plogis(fit + (1.96 * se.fit))})

ggplot(newdatatest_hisp1, aes(x = hisp, y = PredictedProb))+
  geom_ribbon(aes(ymin = LL, ymax = UL)) +geom_line(aes(colour = "hisp"), size=1)

# FamilyDummy 
newdatatest_familysize <- with(mydataset,data.frame(hisp=mean(hisp),PriceCategory=mean(PriceCategory), newcustomer=mean(newcustomer),age=mean(age),MyBestBuy=mean(MyBestBuy),hhincome=mean(hhincome),appliances=mean(appliances),weekend=mean(weekend),familydummy=rep(0:1)))

newdatatest_familysize1 <- cbind(newdatatest_familysize, predict(logit4, newdata = newdatatest_familysize, type="link", se=TRUE))
newdatatest_familysize1
newdatatest_familysize1 <- within(newdatatest_familysize1, {
  PredictedProb <- plogis(fit)
  LL <- plogis(fit - (1.96 * se.fit))
  UL <- plogis(fit + (1.96 * se.fit))})

ggplot(newdatatest_familysize1, aes(x = familydummy, y = PredictedProb))+
  geom_ribbon(aes(ymin = LL, ymax = UL)) +
  geom_line(aes(colour = "familysize"), size=1)

##HHIncome
newdatatest_income <- with(mydataset,data.frame(PriceCategory= mean(PriceCategory), newcustomer=mean(newcustomer),age=mean(age),hisp=mean(hisp),MyBestBuy=mean(MyBestBuy),hhincome=rep(seq(from = 0, to =1312 ,length.out=10)),appliances=mean(appliances),weekend=mean(weekend),familydummy=mean(familydummy)))

hist(log(1+mydataset$hhincome))

newdatatest1 <- cbind(newdatatest_income, predict(logit4, newdata = newdatatest_income, type="link", se=TRUE))
newdatatest1 <- within(newdatatest1, {
  PredictedProb <- plogis(fit)
  LL <- plogis(fit - (1.96 * se.fit))
  UL <- plogis(fit + (1.96 * se.fit))})


ggplot(newdatatest1, aes(x = hhincome, y = PredictedProb))+
  geom_ribbon(aes(ymin = LL, ymax = UL), alpha = .2) +
  geom_line(aes(colour = "hhincome"), size=1)

```



```

```{r}
#Probit
probit1<- glm(Warranty~PriceCategory+newcustomer+age+hisp+MyBestBuy+hhincome+appliances+familysize+weekend,data =mydataset, family=binomial(link="probit"))
summary(probit1)              
### final model
probit2<- glm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer+age+hisp+MyBestBuy+hhincome+appliances+familydummy+weekend,data =mydataset, family=binomial(link="probit"))
summary(probit2)   

probit3<- glm(Warranty~PriceCategory+PriceCategory*appliances+newcustomer+age+hisp+MyBestBuy+log(hhincome+1)+appliances+familysize+weekend,data =mydataset, family=binomial(link="probit"))
summary(probit3)

with(probit2, null.deviance - deviance)
with(probit2, df.null - df.residual)
with(probit2, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

pred = predict(probit2, data=mydataset)
warrenty_prediction <- ifelse(pred >= 0.5,1,0)
misClasificError <- mean(warrenty_prediction != mydataset$Warranty)
print(paste('Accuracy',1-misClasificError))
table(mydataset$Warranty, pred>=0.5)

#we decide to go with logit b/c accuracy is better since accuracy is higher with logit model
```
  
  
  
  
  
  
  
  
  
  
  